MonteCarlo Simulation's of the Covid-19 Pandemic

### 2022-12-10 paper.rmd
formatted paper

---
title: "Paper"
author: "Austin Lackey, Chien Lin and Jin Peng"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Introduction
### Out motivtion for this project is to...

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# useful libraries
library(tidyverse)
library(pracma)
library(minpack.lm)
# read covid data
data <- read_csv("owid-covid-data.csv")
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

```{r}
print(head(data))
```

# Insert More Below....

>>>>

---
title: "MonteCarlo Simulation's of the Covid-19 Pandemic"
author: "Austin Lackey, Chien Lin and Jin Peng"
date: "Tuesday, December 6th, 2022"
output: 
  pdf_document:
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    df_print: paged
    fig_caption: TRUE
    highlight: tango
---
```{r setup, include=FALSE}
# useful libraries
library(tidyverse)
library(pracma)
library(minpack.lm)
# read covid data
data <- read_csv("owid-covid-data.csv")
set.seed(420)
```

# Background and Motivation (Should we do an Abstract?)

*Insert text here*

## Ciufolini and Paolozzi's MonteCarlo Study

*Insert text here*

# Jin: China

*Insert text here*

# Chien: Italy

*Insert text here*

# Austin: Australia

## United States Anomaly

*Insert text here*

# Simulation Analysis Summary

*Insert text here*

# Potential Improvements

*Insert text here*

# Works Cited

- Link to the study:
  - I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
- Link to the covid data used:
  - https://covid19.who.int/
- Source to find the second derivative of fitted function:
  - https://proofwiki.org/wiki/Derivative_of_Error_Function
